---
title: "Tuning function for parameter c1 in sgcca"
author: "Wei Zhang"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_document:
    highlight: pygments
    theme: yeti
    toc: true
    number_sections: true
    df_print: paged
    code_download: false
    toc_float:
      collapsed: yes
    toc_depth: 3
editor_options:
  chunk_output_type: inline    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("code/sgcca_tune.R")
```

This tuning function is inspired by the tuning function of PMACCA. The code can be found in: [tuning-c1-for-sgcca](https://github.com/noblegasss/Tuning-c1-for-sgcca)
The method is also compared with tuning parameter with cross validation 

# Load library

```{r message = F}
library(RGCCA)
library(MASS)
library(tidyverse)
library(purrr)
```

# Simulation two datasets with common latent variables

$$
\begin{aligned}
X&=u w_1^{T}+\epsilon_1, \\
Y&=u w_2^{T}+\epsilon_2
\end{aligned}
$$

```{r}
set.seed(510)
sim.dat <- sim.linear2(n = 100, p = 150, psel = 30)$X
```

We selected the first 30 features as non-zero features.

# Tuning function

```{r}
set.seed(510)
system.time({
  tune.sgcca <- sgcca_tune(sim.dat, scheme = "centroid", nperms = 10)
})
tune.sgcca
```

```{r}
sgcca.m <- sgcca(sim.dat, c1 = rep(tune.sgcca$best_l1))
```

Here we calculated the first canonical correlations with the tuned penalized parameter c1. We can see that most of the zero loadings are shrink to 0.

```{r echo = F}
par(mfrow = c(1,2))
plot(sgcca.m$a$X1, ylab = "loading for X1", pch = 20, col = c(rep("red",30), rep("black",120)))
plot(sgcca.m$a$X2, ylab = "loading for X2", pch = 20, col = c(rep("red",30), rep("black",120)))
```

# Using CV to tue c1

```{r}
set.seed(510)
system.time({
  cv.sgcca <- sgcca_cv(sim.dat, scheme = "centroid", K = 10)
})
print(cv.sgcca)
```


```{r}
sgcca.m <- sgcca(sim.dat, c1 = rep(cv.sgcca$l1))
```


```{r echo = F}
par(mfrow = c(1,2))
plot(sgcca.m$a$X1, ylab = "loading for X1", pch = 20, col = c(rep("red",30), rep("black",120)))
plot(sgcca.m$a$X2, ylab = "loading for X2", pch = 20, col = c(rep("red",30), rep("black",120)))
```



# Without tuning c1

```{r}
sgcca.m2 <- sgcca(sim.dat)
get_corr(sgcca.m2$Y, scheme = "centroid")
```

```{r}
par(mfrow = c(1,2))
plot(sgcca.m2$a$X1, ylab = "loading for X1", pch = 20, col = c(rep("red",30), rep("black",170)))
plot(sgcca.m2$a$X2, ylab = "loading for X2", pch = 20, col = c(rep("red",30), rep("black",170)))
```



# Session Information

```{r}
devtools::session_info()
```

